---
title: "anova"
author: "Tommy Schupp and Cameron Eller"
date: "2024-01-11"
output: html_document
---

```{r}
library(tidyverse)
library(ggplot2)
individuals = read_csv("./individual_communities_and_scores.csv")
pacs = read_csv("./pac_communities_and_scores.csv")
individuals = individuals %>% 
  mutate(party = str_sub(congresspeople, -2, -2)) %>% 
  mutate(community = paste("Community", community))

individuals = individuals %>% 
  drop_na() %>% 
  rename(score = score1) %>% 
  rename(lifetime_score = lifetime_score1)

pacs = pacs %>% 
  drop_na() %>% 
  rename(score = score1) %>% 
  rename(lifetime_score = lifetime_score1) %>% 
  mutate(community = paste("Community", community))

cold_colors <- c("#078D70", "#26CEAA", "#98E8C1", "#7BADE2")
warm_colors <- c("#D52D00", "#EF7627", "#FF9A56", "#D162A4")
warm_colors2 <- c("#D52D00", "#EF7627", "#D162A4", "#B55690", "#A30262", "#5C0029", "#2D080A", "#7C3626", "#FF9A56")

```
Everybody's Lifetime Score 
```{r}
ggplot(individuals, mapping = aes(x = name, y = lifetime_score, color = party))+
  theme_classic()+
  geom_point() +
  coord_cartesian(clip = "off")+
  scale_color_manual(breaks = c("D", "I", "R"), 
                    values = c("blue", "green", "red"),
                    labels=c("Democrat", "Independent", "Republican")) + 
  labs(title = "Congressional Union Scores",
       y = "Union Score")+
  guides(color = guide_legend(title = "Party"))+
  theme(axis.title.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.text.x = element_blank(),
        plot.title = element_text(hjust=0.5))
  
```

ANOVA ASSUMPTIONS

1. each community has a normal population distribution
2. Data are independent
3. Distributions have same variance


Addressing (1): distributions of communities 
```{r}
ggplot(individuals, mapping = aes(x = lifetime_score))+
  theme_bw()+
  geom_histogram(fill="#7BADE2")+
  ggtitle("Individual Union Scores by Community")+
  labs(y = "Number of Congresspeople", x = "Union Score")+
  theme(plot.title = element_text(hjust=0.5),
        strip.background =element_rect(fill="#5988ba"),
        strip.text = element_text(colour = 'white'))+
  facet_wrap(~community)
```

We should probably drop PAC communities 2, 5, 7, 8, 9
```{r}
ggplot(pacs, mapping = aes(x = lifetime_score))+
  theme_bw()+
  geom_histogram(fill=warm_colors[1])+
  ggtitle("PAC Union Scores by Community")+
  labs(y = "Number of Congresspeople", x = "Union Score")+
  theme(plot.title = element_text(hjust=0.5),
        strip.background =element_rect(fill="#9c2302"),
        strip.text = element_text(colour = 'white'))+
  facet_wrap(~community)

```

2. Data are independent 

3. Equal variances
```{r}
ggplot(individuals, mapping = aes(x = community, y = lifetime_score, fill=community))+
  scale_fill_manual(values = cold_colors) +
  geom_boxplot(alpha=1, show.legend = FALSE)+ #alpha is transparency
  labs(title = "Union Score Distributions by Individual Donation Community",
       x = "Walktrap Community",
       y = "Lifetime Union Score")+
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5))
  
```

```{r}
ggplot(pacs, mapping = aes(x = community, y = lifetime_score, fill=community))+
  scale_fill_manual(values = warm_colors2) +
  geom_boxplot(alpha=1, show.legend = FALSE)+ #alpha is transparency
  labs(title = "Lifetime Union Score Distributions by PAC Donation Community",
       x = "Walktrap Community",
       y = "Lifetime Union Score")+
  theme_bw()+
  theme(plot.title = element_text(hjust = 0.5))

```

3. Independence
The data aren't independent. 


Plotting individual means
```{r}
individual_means = individuals %>% 
  group_by(community) %>% 
  summarize(community_mean = mean(lifetime_score))

  ggplot(individual_means, mapping = aes(x = reorder(community, -community_mean), y = community_mean, fill = community))+
    theme_bw()+
    theme(plot.title = element_text(hjust=0.5),
          text=element_text(size=16, family="sans"))+
    scale_fill_manual(values=cold_colors)+
    ggtitle("Individual Network Mean Union Scores")+
    labs(y = "Mean Union Score", x = "Walktrap Community")+
    geom_bar(stat="identity", show.legend = FALSE, color="black")
```

```{r}
individual_anova = aov(lifetime_score ~ community, data = individuals)
summary(individual_anova)

```

Plotting PAC means
```{r}
pacs = pacs %>% 
  group_by(community) %>%
  filter(community != "Community 5") %>%
  filter(community != "Community 2") %>% 
  filter(community != "Community 7") %>% 
  filter(community != "Community 8") %>%
  filter(community != "Community 9") 

pacs_means = pacs %>% 
  summarize(community_mean = mean(lifetime_score))

ggplot(pacs_means, mapping = aes(x = reorder(community, -community_mean), y = community_mean, fill = community))+
  theme_bw()+
  theme(plot.title = element_text(hjust=0.5),
        text=element_text(size=16,  family="sans"))+
  scale_fill_manual(values=warm_colors)+
  ggtitle("PACs Network Mean Union Scores")+
  labs(y = "Mean Union Score", x = "Walktrap Community")+
  geom_bar(stat="identity", show.legend = FALSE, color="black")

```


```{r}
pacs_anova = aov(lifetime_score ~ community, data = pacs)
summary(individual_anova)

```

Then we interpret and we are done. 
